Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2010-10-21 paper/main.tex
Fixed some missing textup macro
Merged in most of Allen's outline.

% Packages added by us
\usepackage{mydefs}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\title{Efficient Parallelization of Sparse Representation for Face Recognition}

@@

@@

We need to define the following soft-thresholding operator for a
scalar $x$ and a scalar $\alpha \geq 0$:
\begin{equation}
\textup{shrink}(x,\alpha) = \textup{sign}(x)\cdot \max \{|x| - \alpha, 0\},
\end{equation}
In practice, this operator will be applied elementwise to a vector $\x$ with a single $\lambda$,
and will be notated as $\texup{shrink}(\x,\alpha).

>>>>

% Packages added by us
\usepackage{amsfonts}
\usepackage{mydefs}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

%\title{Efficient Parallelization of Sparse Representation for Face Recognition}
%\title{Accelerating $\ell_1$-Minimization Using Many-Core CPUs/GPUs \\ and Application to Face Recognition
%\thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}}
\title{Efficient Parallelization of $\ell_1$-Minimization for Face Recognition
\thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}}

@@

[Motivate the paper by an overview about the scope and importance of $\ell_1$-minimization].

[Review the available different algorithms solving $\ell_1$-minimization and $\ell_0$-minimization, please refer to Allen's SIAM paper.]

[Zero in and justify why we choose ALM for our implementation.]

\subsection{Literature review}
[Review the past parallel algorithms for $\ell_1$-minimization. Hopefully there aren't many]

\subsection{Contributions of the paper}
[Can leave empty until later.]

@@

We need to define the following soft-thresholding operator for a
scalar $x$ and a scalar $\alpha \geq 0$:
\begin{equation}
\textup{shrink}(x,\alpha) = \textup{sign}(x)\cdot \max \{|x| - \alpha, 0\},
\end{equation}
In practice, this operator will be applied elementwise to a vector $\x$ with a single $\lambda$,
and will be notated as $\textup{shrink}(\x,\alpha)$.
